### 2021-10-22 documentos/pce.tex
Well, it's doing something.
Fixed everything.

Consider the linear operations that simply attenuate the Pauli components of 
a multiqubit system:
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\end{equation}
These operations are diagonal in the basis $\left\{ 2^{-N/2}\sigma_{\vec \alpha} \right\}$, this follows straightforwardly from \eref{eq:sigma_property}, in fact, the diagonal components are exactly $\taus$, this is $\hat \mcE=\diag(\taus)$. Additionally, they are unital (leave invariant the complete mixture), in fact, as we will show later, they belong to the subset of unital channels that can be written as convex combinations of unitary channels.
 \cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
frases. También debemos tener un nombre pues lo de la diagonazliación funciona
para eso y quizá también seran relevantes para la parte de decoherencia}
\ddnote{De momento no he encontrado alguna reference, para qubits si, pero para
los generales no, estoy checando de nuevo el paper de Ruskai para entender que
tanto se solapan, a ver si puedo decir algo}.
For the operation to preserve the trace of the density matrix, we require that 
$\tau_{\vec 0}=1$. 
A Pauli component erasing (PCE) operation is a Pauli diagonal operation
%  A linear operation 
% $\mcE$ 
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation} \label{eq:PCE_definition}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
It is worth noticing that not all PCE maps are quantum operations. For single 
qubits, if just one of the $\taus=0$, the complete positivity condition 
is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
in this article to determine which $\taus$ lead to a valid quantum map.

@@

\begin{figure} % {{{
\begin{center}
\begin{tikzpicture}[x=0.5cm, y=0.5cm] % {{{
\pgfmathsetmacro{\unitstep}{3.5}
% Coordenadas   {{{
\node at (-0.6,0.5) {(a)} ;
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_0$} ;
\begin{scope}[shift={(0,-1)}]
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_1$} ;
\end{scope}
\begin{scope}[shift={(0,-2)}]
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_2$} ;
\end{scope}
\begin{scope}[shift={(0,-3)}]
\draw (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_3$} ;
\end{scope} % }}}
\begin{scope}[shift={(1*\unitstep,0)}] % Identity {{{
% \begin{scope}[shift={(\unitstep*2,0)}]
\node at (-0.6,0.5) {(b)} ;
\fill[black] (0,0) rectangle (1,1);
\draw (0,0) rectangle (1,1);
\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(2*\unitstep,0)}] % Dephasing {{{
\node at (-0.6,0.5) {(c)} ;
\fill[black] (0,0) rectangle (1,1);
\draw (0,0) rectangle (1,1);
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(3*\unitstep,0)}] % Depolarization {{{
\node at (-0.6,0.5) {(d)} ;
\fill[black] (0,0) rectangle (1,1);
\draw (0,0) rectangle (1,1);
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(4*\unitstep,0)}] % (e) canal malo {{{
\node at (-0.6,0.5) {(e)} ;
\fill[black] (0,0) rectangle (1,1);
\draw (0,0) rectangle (1,1);
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\end{tikzpicture} % }}}
\end{center}
	\caption{In (a) we introduce the positions of the single 
qubit diagrams, so that each square corresponds to a single 
$\tau_{\alpha}$, $\alpha=0,1,2,3$. The diagrams in 
(b), (c) and (d) correspond to the identity map, \cpnote{bit flip ao algo asi}, and 
total depolarization, respectively. In (e) we show a map that only erases the component
$r_1$ and thus does not correspond to a quantum operation.}
	\label{fig:one:qubit:examples}
\end{figure} % }}}

\begin{figure} % {{{
\begin{tikzpicture}[x=0.55cm, y=0.55cm] % {{{
\pgfmathsetmacro{\unitstep}{5.2}
\begin{scope}[shift={(0*\unitstep,0)}] % Coordenadas {{{
\node at (-0.5,0.5) {(a)} ;
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw (0,0) rectangle (1,1); 
          \node at (0.5,0.5) {\scalebox{.8}{$\tau_{(\y,\x)}$}};
         \end{scope}
%         \node at (0,-\y) (input\y) {$i_\y$};
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (input\y) -- (block\y);
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
\end{scope} % }}}
\begin{scope}[shift={(1*\unitstep,0)}] % Good channel {{{
\node at (-0.5,0.5) {(b)} ;
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw (0,0) rectangle (1,1); 
%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
         \end{scope}
%         \node at (0,-\y) (input\y) {$i_\y$};
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (input\y) -- (block\y);
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(2*\unitstep,0)}] % Good channel {{{
\node at (-0.5,0.5) {(c)} ;
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw (0,0) rectangle (1,1); 
%           \node at (0.5,0.5) {$\tau_{\y,\x}$};
         \end{scope}
%         \node at (0,-\y) (input\y) {$i_\y$};
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (input\y) -- (block\y);
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\end{tikzpicture} % }}}
	\caption{In (a) we introduce the
positions of two qubit diagrams. The diagrams in 
(b) corresponds to a quantum channel that results from the tensor product of
bit flip channels in each qubit [see \fref{fig:one:qubit:examples}(c)],
and in (c) a diagram of a map that is not a quantum channel is presented.}
	\label{fig:two:qubit:examples}
\end{figure} % }}}

>>>>

Consider the linear operations that simply attenuate the Pauli components of 
a multiqubit system:
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\label{eq:definition:Pauli}
\end{equation}
These operations are diagonal in the basis $\left\{ 2^{-N/2}\sigma_{\vec \alpha} \right\}$, this follows straightforwardly from \eref{eq:sigma_property}, in fact, the diagonal components are exactly $\taus$, this is $\hat \mcE=\diag(\taus)$. Additionally, they are unital (leave invariant the complete mixture), in fact, as we will show later, they belong to the subset of unital channels that can be written as convex combinations of unitary channels.
 \cpnote{davalos, dale aca un pequeño rollo relevante quiza de una o dos
frases. También debemos tener un nombre pues lo de la diagonazliación funciona
para eso y quizá también seran relevantes para la parte de decoherencia}
\ddnote{De momento no he encontrado alguna reference, para qubits si, pero para
los generales no, estoy checando de nuevo el paper de Ruskai para entender que
tanto se solapan, a ver si puedo decir algo}.
For the operation to preserve the trace of the density matrix, we require that 
$\tau_{\vec 0}=1$. 
A Pauli component erasing (PCE) operation is a Pauli diagonal operation
%  A linear operation 
% $\mcE$ 
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation} \label{eq:PCE_definition}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
It is worth noticing that not all PCE maps are quantum operations. For single 
qubits, if just one of the $\taus=0$, the complete positivity condition 
is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
in this article to determine which $\taus$ lead to a valid quantum map.

@@

\begin{figure} % {{{
\begin{center}
\begin{tikzpicture}[x=0.5cm, y=0.5cm] % {{{
\pgfmathsetmacro{\unitstep}{3.5}
% Coordenadas   {{{
\node at (-0.6,0.5) {(a)} ;
\draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_0$} ;
\begin{scope}[shift={(0,-1)}]
\draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_1$} ;
\end{scope}
\begin{scope}[shift={(0,-2)}]
\draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_2$} ;
\end{scope}
\begin{scope}[shift={(0,-3)}]
\draw[black!10] (0,0) rectangle (1,1); \node at (0.5,0.5) {$\tau_3$} ;
\end{scope} 
\draw (0,-3) rectangle (1,1); 
\begin{scope}[shift={(1*\unitstep,0)}] % Identity {{{
% \begin{scope}[shift={(\unitstep*2,0)}]
\node at (-0.6,0.5) {(b)} ;
\fill[black] (0,0) rectangle (1,1);
\draw[black!10] (0,0) rectangle (1,1);
\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\draw (0,-3) rectangle (1,1); 
\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(2*\unitstep,0)}] % Dephasing {{{
\node at (-0.6,0.5) {(c)} ;
\fill[black] (0,0) rectangle (1,1);
% \draw (0,0) rectangle (1,1);
\draw[black!10] (0,0) rectangle (1,1);
\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\draw (0,-3) rectangle (1,1); 
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(3*\unitstep,0)}] % Depolarization {{{
\node at (-0.6,0.5) {(d)} ;
\fill[black] (0,0) rectangle (1,1);
% \draw (0,0) rectangle (1,1);
\draw[black!10] (0,0) rectangle (1,1);
\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\draw (0,-3) rectangle (1,1); 
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(4*\unitstep,0)}] % (e) canal malo {{{
\node at (-0.6,0.5) {(e)} ;
\fill[black] (0,0) rectangle (1,1);
% \draw (0,0) rectangle (1,1);
\draw[black!10] (0,0) rectangle (1,1);
\begin{scope}[shift={(0,-1)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \draw[black!10] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-1)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-2)}] \draw (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
% \begin{scope}[shift={(0,-3)}] \draw (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\end{tikzpicture} % }}}
\end{center}
	\caption{In (a) we introduce the positions of the single 
qubit diagrams, so that each square corresponds to a single 
$\tau_{\alpha}$, $\alpha=0,1,2,3$. The diagrams in 
(b), (c) and (d) correspond to the identity map, \cpnote{bit flip ao algo asi}, and 
total depolarization, respectively. In (e) we show a map that only erases the component
$r_1$ and thus does not correspond to a quantum operation.}
	\label{fig:one:qubit:examples}
\end{figure} % }}}

\begin{figure} % {{{
\begin{tikzpicture}[x=0.55cm, y=0.55cm] % {{{
\pgfmathsetmacro{\unitstep}{5.2}
\begin{scope}[shift={(0*\unitstep,0)}] % Coordenadas {{{
\node at (-0.5,0.5) {(a)} ;
% \cuadritotikz{}
    \foreach \x in {0,1,2,3} {
      \foreach \y in {0,1,2,3} {
        \begin{scope}[shift={(\x,-\y)}] 
          \draw[black!10] (0,0) rectangle (1,1); 
%           \draw (0,0) rectangle (1,1); 
          \node at (0.5,0.5) {\scalebox{.8}{$\tau_{(\y,\x)}$}};
         \end{scope}
%         \node at (0,-\y) (input\y) {$i_\y$};
%         \node[block] at (2,-\y) (block\y) {$f_\y$};
%         \draw[->] (input\y) -- (block\y);
%         \draw[->] (block\y.east) -- +(0.5,0);
    }
    }
 \draw (0,-3) rectangle (4,1);
\end{scope} % }}}
\begin{scope}[shift={(1*\unitstep,0)}] % Good channel {{{
\node at (-0.5,0.5) {(b)} ;
\cuadritotikz{}
%     \foreach \x in {0,1,2,3} {
%       \foreach \y in {0,1,2,3} {
%         \begin{scope}[shift={(\x,-\y)}] 
%           \draw (0,0) rectangle (1,1); 
% %           \node at (0.5,0.5) {$\tau_{\y,\x}$};
%          \end{scope}
% %         \node at (0,-\y) (input\y) {$i_\y$};
% %         \node[block] at (2,-\y) (block\y) {$f_\y$};
% %         \draw[->] (input\y) -- (block\y);
% %         \draw[->] (block\y.east) -- +(0.5,0);
%     }
%     }
\begin{scope}[shift={(0,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(3,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(3,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\begin{scope}[shift={(2*\unitstep,0)}] % Good channel {{{
\node at (-0.5,0.5) {(c)} ;
\cuadritotikz{}
%     \foreach \x in {0,1,2,3} {
%       \foreach \y in {0,1,2,3} {
%         \begin{scope}[shift={(\x,-\y)}] 
%           \draw (0,0) rectangle (1,1); 
% %           \node at (0.5,0.5) {$\tau_{\y,\x}$};
%          \end{scope}
% %         \node at (0,-\y) (input\y) {$i_\y$};
% %         \node[block] at (2,-\y) (block\y) {$f_\y$};
% %         \draw[->] (input\y) -- (block\y);
% %         \draw[->] (block\y.east) -- +(0.5,0);
%     }
%     }
\begin{scope}[shift={(0,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(0,-1)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,0)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,-2)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\begin{scope}[shift={(2,-3)}] \fill[black] (0,0) rectangle (1,1); \end{scope}
\end{scope} % }}}
\end{tikzpicture} % }}}
	\caption{In (a) we introduce the
positions of two qubit diagrams. The diagrams in 
(b) corresponds to a quantum channel that results from the tensor product of
bit flip channels in each qubit [see \fref{fig:one:qubit:examples}(c)],
and in (c) a diagram of a map that is not a quantum channel is presented.}
	\label{fig:two:qubit:examples}
\end{figure} % }}}
